How to compute the fusion product of MV cycles in type A

### 2021-02-19 draft.tex
double yup

    \jcom{Instead of $\TT^+$ maybe a different letter would be best? I'm moved all $\lambda, \mu$ to upper indices for consistency (except for $ \cW_\mu, T_\mu$) and also to let us put $ s $ or $ \AA$ in the lower index.  I haven't been very consistent about $ \AA $ vs $ \CC$.  Which do you prefer?}

@@

\subsection{Old stuff}
\jcom{I'm going to delete everything below here in this section, if that is ok with you.}

>>>>

    \jcom{Instead of $\TT^+$ maybe a different letter would be best? I'm moved all $\lambda, \mu$ to upper indices for consistency (except for $ \cW_\mu, \TT_\mu$) and also to let us put $ s $ or $ \AA$ in the lower index.  I haven't been very consistent about $ \AA $ vs $ \CC$.  Which do you prefer?}

@@

\subsection{Old stuff}
\jcom{I'm going to delete everything below here in this section, if that is ok with you.}
\acom{Yup!}
